myeloma

### 2023-04-05 analyses/optimDialysis.Rmd
File Changes

---
title: "aids"
output: html_document
params:
  epo: 200
  patience: 5
  iteration: 2
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
library(reticulate)
eval_aids<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0 #10^-7

@@

```{r aidsPrep,eval=T}

library(MASS)
aids<-Aids2

aids<-aids[which(aids$T.categ=="hs"),]
aids<-aids[which(aids$sex=="M"),]

stattt<-as.factor(aids$status)

levels(stattt)<-c(0,1)
preData<-data.frame(#sex=as.factor(aids$sex),
                    #tcat=as.factor(aids$T.categ),
                    age=as.numeric(aids$age),
                    time=as.numeric(as.numeric(aids$death)-as.numeric(aids$diag)),
                    status=as.numeric(stattt)-1
)
preData<-na.omit(preData)

@@

saveRDS(res$test,"aidsTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"aidsCV.rds")

@@

```{r setFixedHyperparameters}

klist<-readRDS("aidsCV.rds")

@@

lr=c(0.001,0.0005)
drpt=c(0.25,0.1)
layer1=c(20,50,100)
layer2=c(10,25,50)
nBatch=c(100,500,1000)
actv=c("relu","linear","tanh")#
alp=c(0,0.5,1)

lr=c(0.001)
drpt=c(0.25)
layer1=c(20)
layer2=c(10)
nBatch=c(1000,100)
actv=c("relu")#
alp=c(0)

@@

```{r hyperOpDsurv}

@@

klist<-readRDS("aidsCV.rds")
test<-readRDS("aidsTest.rds")
source_python('src/dsurv.py')
bestDS<-optimDeepSurv(klist,test,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,nBatch,actv)

@@

```{r optimDeepHit,eval=reoptimize}

@@

klist<-readRDS("aidsCV.rds")
test<-readRDS("aidsTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

@@

```{r hyperopcbnn,eval=reoptimize}

@@

klist<-readRDS("aidsCV.rds")
test<-readRDS("aidsTest.rds")

@@

```{r winners}
winners<-list(cbnn=cbnnPerformance,
              ds=bestDS,
              dh=bestDH)

saveRDS(winners,"aidsWins.rds")

@@

winners<-readRDS("aidsWins.rds")

klist<-readRDS("aidsCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)
#data$time<-data$time/max(data$time)

@@

  fullTest<-readRDS("aidsTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100aidsBrier.rds')
  saveRDS(cScore,'results/100aidscidx.rds')
  pos=pos+1

@@

```{r plotaids}

BrierIPAList<-readRDS('results/100aidsBrier.rds')

@@

ipa+coord_cartesian(ylim=c(-0.1,0.5))
#end_time-start_time

@@

>>>>

---
title: "dialysis"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 100
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
library(reticulate)
eval_dialysis<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0 #10^-7

@@

```{r dialysisPrep,eval=FALSE,hide=FALSE}

dialysis<-readRDS("dialysis.rds")

data <- dialysis[, c(1,2,3,4,7,6,5)]
colnames(data)[7]<-"status"

#RcmdrPlugin.survival/html/Dialysis.html

smallCenters<-as.numeric(names(which( table(data$center)<30)))
toRemove<-c()
for(i in 1:nrow(data)){
  if(data$center[i] %in% smallCenters){
    toRemove<-append(toRemove,i)
  }

}
#data<-data[-toRemove,]

preData<-data.frame(#center=as.factor(data$center),
                    age=as.numeric(data$age),
                    #begin=as.numeric(data$begin),
                    disease=as.factor(data$disease),
                    time=data$time,
                    status=data$status)

@@

saveRDS(res$test,"dialysisTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"dialysisCV.rds")

@@

```{r setFixedHyperparameters,eval=FALSE,hide=FALSE}

klist<-readRDS("dialysisCV.rds")

@@

lr=c(0.001,0.01)
drpt=c(0.01,0.05,0.1)
layer1=c(50,75,100)
layer2=c(10,25,50)
nBatch=c(100,500)
actv=c("relu","linear")#
alp=c(0,0.5,1)
# 
# lr=c(0.001)
# drpt=c(0.25)
# layer1=c(20)
# layer2=c(10)
# nBatch=c(1000,100)
# actv=c("relu")#
# alp=c(0)

@@

```{r hyperOpDsurv,eval=FALSE,hide=FALSE}

@@

klist<-readRDS("dialysisCV.rds")
test<-readRDS("dialysisTest.rds")
source_python('src/dsurv.py')
bestDS<-optimDeepSurv(klist,test,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,nBatch,actv)

@@

```{r optimDeepHit,eval=FALSE,hide=FALSE}

@@

klist<-readRDS("dialysisCV.rds")
test<-readRDS("dialysisTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

@@

```{r hyperopcbnn,eval=FALSE,hide=FALSE}

@@

klist<-readRDS("dialysisCV.rds")
test<-readRDS("dialysisTest.rds")

@@

```{r winners,eval=FALSE,hide=FALSE}
winners<-list(cbnn=cbnnPerformance,
              ds=bestDS,
              dh=bestDH)

saveRDS(winners,"dialysisWins.rds")

@@

winners<-readRDS("dialysisWins.rds")

klist<-readRDS("dialysisCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)
#data$time<-data$time/max(data$time)

@@

  fullTest<-readRDS("dialysisTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100dialysisBrier.rds')
  saveRDS(cScore,'results/100dialysiscidx.rds')
  pos=pos+1

@@

```{r plotdialysis}

BrierIPAList<-readRDS('results/100dialysisBrier.rds')

@@

ipa+coord_cartesian(ylim=c(-0.1,0.2))
#end_time-start_time

@@

```{r}

cidxList<-readRDS('results/100dialysiscidx.rds')

temp<-melt(setDT(as.data.frame(cidxList[[1]])), id.vars = c("times"), variable.name = "model")
cidxSims=data.frame(model=temp$model,times=temp$times)

count=1
for(sim in cidxList){
  cidxSims<-cbind(cidxSims, melt(setDT(as.data.frame(sim)), id.vars = c("times"), variable.name = "model")$value)

  count<-count+1
}

cidxSummary<-statCalcSim(cidxSims)
cidxC<-plotPerformance(cidxSummary,method="C-Index",iterations=iteration  )
cidxC

### 2023-04-05 analyses/optimFlchain.Rmd
File Changes

---
title: "dialysis"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 100
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
library(reticulate)
eval_dialysis<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0 #10^-7

@@

```{r dialysisPrep,eval=FALSE,hide=FALSE}

dialysis<-readRDS("dialysis.rds")

data <- dialysis[, c(1,2,3,4,7,6,5)]
colnames(data)[7]<-"status"

#RcmdrPlugin.survival/html/Dialysis.html

smallCenters<-as.numeric(names(which( table(data$center)<30)))
toRemove<-c()
for(i in 1:nrow(data)){
  if(data$center[i] %in% smallCenters){
    toRemove<-append(toRemove,i)
  }

}
#data<-data[-toRemove,]

preData<-data.frame(#center=as.factor(data$center),
                    age=as.numeric(data$age),
                    #begin=as.numeric(data$begin),
                    disease=as.factor(data$disease),
                    time=data$time,
                    status=data$status)

@@

saveRDS(res$test,"dialysisTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"dialysisCV.rds")

@@

klist<-readRDS("dialysisCV.rds")

@@

lr=c(0.001,0.01)
drpt=c(0.01,0.05,0.1)
layer1=c(50,75,100)
layer2=c(10,25,50)
nBatch=c(100,500)
actv=c("relu","linear")#
alp=c(0,0.5,1)
# 
# lr=c(0.001)
# drpt=c(0.25)
# layer1=c(20)
# layer2=c(10)
# nBatch=c(1000,100)
# actv=c("relu")#
# alp=c(0)

@@

    #paramTrials$IPA[i]<-mean(tempRes)
    #paramTrials$IPAse[i]<-sd(tempRes)
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("dialysisCV.rds")
test<-readRDS("dialysisTest.rds")
source_python('src/dsurv.py')
bestDS<-optimDeepSurv(klist,test,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,nBatch,actv)

@@

    #paramTrials$IPA[i]<-mean(tempRes)
    #paramTrials$IPAse[i]<-sd(tempRes)
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("dialysisCV.rds")
test<-readRDS("dialysisTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

@@

    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i,"out of ",nrow(paramTrials)))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("dialysisCV.rds")
test<-readRDS("dialysisTest.rds")

@@

saveRDS(winners,"dialysisWins.rds")

@@

winners<-readRDS("dialysisWins.rds")

klist<-readRDS("dialysisCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)
#data$time<-data$time/max(data$time)

start_time <- Sys.time()
BrierIPAList<-list()
cScore<-list()
pos<-1

@@

  fullTest<-readRDS("dialysisTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

@@

  linModelTrain<-as.data.frame(rbind(train,val))
  #valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)#rbind(train,val)
  #valcb$offset<-0
  #valcbtensor<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),as.matrix(valcb[,ncol(valcb),drop=F])),as.matrix(valcb[,ncol(valcb)-1,drop=F]))
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 20
  )

@@

  ############################
  ###Brier Score
  ############################  
  brierFinalResults <- Score(list("Cox_Lin" = cox,'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,'DeepHit'=deephitCleaned,
                                  'CBNN_Poly'=annProperpoly),
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100dialysisBrier.rds')
  saveRDS(cScore,'results/100dialysiscidx.rds')
  pos=pos+1

@@

```{r plotdialysis}

BrierIPAList<-readRDS('results/100dialysisBrier.rds')

@@

ipa+coord_cartesian(ylim=c(-0.1,0.2))
#end_time-start_time

@@

cidxList<-readRDS('results/100dialysiscidx.rds')

>>>>

---
title: "flchain"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 100
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
library(reticulate)
eval_flchain<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0 #10^-7

@@

```{r flchainPrep,eval=FALSE,hide=FALSE}

library(survival)
flchain<-flchain

preData<-data.frame(age=as.numeric(flchain$age),
                    #sampyr=as.numeric(flchain$sample.yr),
                    sex=as.factor(flchain$sex),
                    flc=as.numeric(flchain$kappa)+as.numeric(flchain$lambda),
                    #batch=as.factor(flchain$flc.grp),
                    creatine=as.numeric(flchain$creatinine),
                    mgus=as.numeric(flchain$mgus),
                    time=as.numeric(flchain$futime),
                    status=as.numeric(flchain$death)
)

@@

##saveRDS(res$test,"flchainTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
##saveRDS(klist,"flchainCV.rds")

@@

klist<-readRDS("flchainCV.rds")

@@

lr=c(0.001,0.01)
drpt=c(0.01,0.05,0.1)
layer1=c(50,75,100)
layer2=c(10,25,50)
nBatch=c(100,500)
actv=c("relu","linear")#
alp=c(0,0.5,1)

# 
# lr=c(0.001)
# drpt=c(0.25)
# layer1=c(20)
# layer2=c(10)
# nBatch=c(1000,100)
# actv=c("relu")#
# alp=c(0)

@@

    #paramTrials$IPA[i]<-mean(tempRes)
    #paramTrials$IPAse[i]<-sd(tempRes)
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    ##saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("flchainCV.rds")
test<-readRDS("flchainTest.rds")
source_python('src/dsurv.py')
bestDS<-optimDeepSurv(klist,test,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,nBatch,actv)

@@

    #paramTrials$IPA[i]<-mean(tempRes)
    #paramTrials$IPAse[i]<-sd(tempRes)
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    ##saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("flchainCV.rds")
test<-readRDS("flchainTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

@@

    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    ##saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i,"out of ",nrow(paramTrials)))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("flchainCV.rds")
test<-readRDS("flchainTest.rds")

@@

##saveRDS(winners,"flchainWins.rds")

@@

winners<-readRDS("flchainWins.rds")

klist<-readRDS("flchainCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)
#data$time<-data$time/max(data$time)

start_time <- Sys.time()
BrierIPAList<-list()
cScore<-list()
AUClist<-list()
pos<-1

@@

  fullTest<-readRDS("flchainTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

@@

  linModelTrain<-as.data.frame(rbind(train,val))
  #valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)#rbind(train,val)
  #valcb$offset<-0
  #valcbtensor<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),as.matrix(valcb[,ncol(valcb),drop=F])),as.matrix(valcb[,ncol(valcb)-1,drop=F]))
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 82
  )

@@

  ############################
  ###Brier Score
  ############################  
  brierFinalResults <- Score(list("Cox_Lin" = cox,'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,'DeepHit'=deephitCleaned,
                                  'CBNN_Poly'=annProperpoly),
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = c("auc", "brier"), contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score
  AUClist[[pos]]<-brierFinalResults$AUC$score

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100flchainBrier.rds')
  saveRDS(cScore,'results/100flchaincidx.rds')
  saveRDS(AUClist,'results/100flchainAuc.rds')
  pos=pos+1

@@

```{r plotflchain}

BrierIPAList<-readRDS('results/100flchainBrier.rds')

@@

ipa+coord_cartesian(ylim=c(-0.1,0.5))
#end_time-start_time

```{r auc}

AUClist<-readRDS('results/100flchainAuc.rds')
aucSims=data.frame(model=AUClist[[1]]$model,times=AUClist[[1]]$times)
for(sim in AUClist){
   aucSims<-cbind(aucSims,sim$AUC)

}
aucSummary<-statCalcSim(aucSims)
auc<-plotPerformance(aucSummary,method="AUC",iterations=iteration )

auc

@@

cidxList<-readRDS('results/100flchaincidx.rds')

### 2023-04-05 analyses/optimMyeloma.Rmd
File Changes

---
title: "flchain"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 100
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
library(reticulate)
eval_flchain<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0 #10^-7

@@

reoptimize=T

@@

```{r flchainPrep,eval=FALSE,hide=FALSE}

library(survival)
flchain<-flchain

preData<-data.frame(age=as.numeric(flchain$age),
                    #sampyr=as.numeric(flchain$sample.yr),
                    sex=as.factor(flchain$sex),
                    flc=as.numeric(flchain$kappa)+as.numeric(flchain$lambda),
                    #batch=as.factor(flchain$flc.grp),
                    creatine=as.numeric(flchain$creatinine),
                    mgus=as.numeric(flchain$mgus),
                    time=as.numeric(flchain$futime),
                    status=as.numeric(flchain$death)
)

@@

##saveRDS(res$test,"flchainTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
##saveRDS(klist,"flchainCV.rds")

@@

klist<-readRDS("flchainCV.rds")

@@

lr=c(0.001,0.01)
drpt=c(0.01,0.05,0.1)
layer1=c(50,75,100)
layer2=c(10,25,50)
nBatch=c(100,500)
actv=c("relu","linear")#
alp=c(0,0.5,1)

# 
# lr=c(0.001)
# drpt=c(0.25)
# layer1=c(20)
# layer2=c(10)
# nBatch=c(1000,100)
# actv=c("relu")#
# alp=c(0)

@@

klist<-readRDS("flchainCV.rds")
test<-readRDS("flchainTest.rds")
source_python('src/dsurv.py')
bestDS<-optimDeepSurv(klist,test,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,nBatch,actv)

@@

klist<-readRDS("flchainCV.rds")
test<-readRDS("flchainTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

@@

klist<-readRDS("flchainCV.rds")
test<-readRDS("flchainTest.rds")

@@

##saveRDS(winners,"flchainWins.rds")

@@

winners<-readRDS("flchainWins.rds")

klist<-readRDS("flchainCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)
#data$time<-data$time/max(data$time)

@@

  fullTest<-readRDS("flchainTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

@@

  linModelTrain<-as.data.frame(rbind(train,val))
  #valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)#rbind(train,val)
  #valcb$offset<-0
  #valcbtensor<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),as.matrix(valcb[,ncol(valcb),drop=F])),as.matrix(valcb[,ncol(valcb)-1,drop=F]))
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 82
  )

@@

  ############################
  ###Brier Score
  ############################  
  brierFinalResults <- Score(list("Cox_Lin" = cox,'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,'DeepHit'=deephitCleaned,
                                  'CBNN_Poly'=annProperpoly),
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = c("auc", "brier"), contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score
  AUClist[[pos]]<-brierFinalResults$AUC$score

@@

  tempTims<-   as.numeric(colnames(annProperpoly))
  tempTims<-head(tempTims, -1)
  tempTims<-tail(tempTims, -1)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=length(riskList)+1)
  et_train<-as.matrix(tempTrain)[,c(ncol(tempTrain),ncol(tempTrain)-1)]
  et_test<-as.matrix(fullTest[,c(ncol(fullTest),ncol(fullTest)-1)])
  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'cbnn')
  cScoreTemp[,1]<- tempTims

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100flchainBrier.rds')
  saveRDS(cScore,'results/100flchaincidx.rds')
  saveRDS(AUClist,'results/100flchainAuc.rds')
  pos=pos+1

@@

```{r plotflchain}

BrierIPAList<-readRDS('results/100flchainBrier.rds')

@@

ipa+coord_cartesian(ylim=c(-0.1,0.5))
#end_time-start_time

@@

AUClist<-readRDS('results/100flchainAuc.rds')
aucSims=data.frame(model=AUClist[[1]]$model,times=AUClist[[1]]$times)
for(sim in AUClist){
   aucSims<-cbind(aucSims,sim$AUC)

@@

cidxList<-readRDS('results/100flchaincidx.rds')

@@

>>>>

---
title: "myeloma"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 100
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

@@

```{r setup, include=T}
set.seed(12)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
library(reticulate)
eval_myeloma<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0 #10^-7

@@

reoptimize=FALSE

@@

```{r myelomaPrep,eval=FALSE,hide=FALSE}

library(survival)

data("cancer", package="survival")

preData<-data.frame(year=as.numeric(myeloma$year),
                    entry=as.numeric(myeloma$entry),
                    time=as.numeric(myeloma$futime),
                    status=as.numeric(myeloma$death)
)

@@

#saveRDS(res$test,"myelomaTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
#saveRDS(klist,"myelomaCV.rds")

@@

klist<-readRDS("myelomaCV.rds")

@@

lr=c(0.001,0.01)
drpt=c(0.01,0.05,0.1)
layer1=c(50,75,100)
layer2=c(10,25,50)
nBatch=c(100,500)
actv=c("relu","linear")#
alp=c(0,0.5,1)
# 
# lr=c(0.001)
# drpt=c(0.25)
# layer1=c(20)
# layer2=c(10)
# nBatch=c(1000,100)
# actv=c("relu")#
# alp=c(0)

@@

klist<-readRDS("myelomaCV.rds")
test<-readRDS("myelomaTest.rds")
source_python('src/dsurv.py')
bestDS<-optimDeepSurv(klist,test,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,nBatch,actv)

@@

klist<-readRDS("myelomaCV.rds")
test<-readRDS("myelomaTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

@@

klist<-readRDS("myelomaCV.rds")
test<-readRDS("myelomaTest.rds")

@@

#saveRDS(winners,"myelomaWins.rds")

@@

winners<-readRDS("myelomaWins.rds")

klist<-readRDS("myelomaCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)
#data$time<-data$time/max(data$time)

@@

  fullTest<-readRDS("myelomaTest.rds")

  if(sum(fullTest$time>max(train$time))>0){next }

  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

@@

  linModelTrain<-as.data.frame(rbind(train,val))
  #valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)#rbind(train,val)
  #valcb$offset<-0
  #valcbtensor<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),as.matrix(valcb[,ncol(valcb),drop=F])),as.matrix(valcb[,ncol(valcb)-1,drop=F]))
  times<-seq(from=min(train$time),
             to=max(train$time),
             length.out = 82
  )

@@

  ############################
  ###Brier Score
  ############################  
  brierFinalResults <- Score(list("Cox_Lin" = cox,'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,'DeepHit'=deephitCleaned,
                                  'CBNN_Poly'=annProperpoly),
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics =c("auc", "brier"), contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score
  AUClist[[pos]]<-brierFinalResults$AUC$score

@@

  tempTims<-   as.numeric(colnames(annProperpoly))
  tempTims<-head(tempTims, -1)
  tempTims<-tail(tempTims, -1)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=length(riskList)+1)
  et_train<-as.matrix(tempTrain)[,c(ncol(tempTrain),ncol(tempTrain)-1)]
  et_test<-as.matrix(fullTest[,c(ncol(fullTest),ncol(fullTest)-1)])

  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'cbnn')
  cScoreTemp[,1]<- tempTims

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )

  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100myelomaBrier.rds')
  saveRDS(cScore,'results/100myelomacidx.rds')
  saveRDS(AUClist,'results/100myelomaAuc.rds')
  pos=pos+1

@@

```{r plotmyeloma}

BrierIPAList<-readRDS('results/100myelomaBrier.rds')
toRemove<-c()
cleaned<-list()
for(i in 1:length(BrierIPAList)){
  if(nrow(BrierIPAList[[i]])>110){
    cleaned[[length(cleaned)+1]]<-BrierIPAList[[i]]
  }
}

BrierIPAList<-cleaned

@@

ipa+coord_cartesian(ylim=c(-0.8,0.4))
#end_time-start_time

@@

AUClist<-readRDS('results/100myelomaAuc.rds')
aucSims=data.frame(model=AUClist[[1]]$model,times=AUClist[[1]]$times)
for(sim in AUClist){
   aucSims<-cbind(aucSims,sim$AUC)

@@

cidxList<-readRDS('results/100myelomacidx.rds')

@@

#https://scikit-survival.readthedocs.io/en/stable/user_guide/evaluating-survival-models.html
```
